Analyses

### 2021-05-07 report/draft.Rmd
add exploratory results

## Pre-Registered Hypotheses
\newpage 
\blandscape 
```{r results-hs, out.width = "95%", fig.align = 'center', fig.cap = "\\label{fig:results}Results"}
include_graphics(here("report/figures", "save-patchwork-results-1.png"))
```
\elandscape

@@

>>>>

## Pre-Registered Hypotheses
\newpage 
\blandscape 
```{r results-main, out.width = "95%", fig.align = 'center', fig.cap = "\\label{fig:results}Results"}
include_graphics(here("report/figures", "save-patchwork-results-1.png"))
```
\elandscape

@@

**_Ideology_**
\newpage 
\blandscape 
```{r results-ideology, out.width = "95%", fig.align = 'center', fig.cap = "\\label{fig:results-ideology}Results: Interaction with Ideology"}
include_graphics(here("report/figures", "explore-ideology-1.png"))
```
\elandscape

**_Willingness to Accept Compromises_**
\newpage 
\blandscape 
```{r results-wtac, out.width = "95%", fig.align = 'center', fig.cap = "\\label{fig:results-wtac}Results: Interaction with Willingness to Accept Compromise"}
include_graphics(here("report/figures", "explore-wtac-1.png"))
```
\elandscape

**_Attitude towards Women in Politics_**
\newpage 
\blandscape 
```{r results-women-politics, out.width = "95%", fig.align = 'center', fig.cap = "\\label{fig:results-women-politics}Results: Interaction with Attitudes towards Women in Politics"}
include_graphics(here("report/figures", "explore-women-politics-1.png"))
```
\elandscape

**_Position on Political Issues_**
\newpage 
\blandscape 
```{r results-covid, out.width = "95%", fig.align = 'center', fig.cap = "\\label{fig:results-covid}Results: Interaction with Position on COVID-19"}
include_graphics(here("report/figures", "explore-covid-1.png"))
```
\elandscape

\newpage 
\blandscape 
```{r results-defense, out.width = "95%", fig.align = 'center', fig.cap = "\\label{fig:results-defense}Results: Interaction with Position on Defense"}
include_graphics(here("report/figures", "explore-defense-1.png"))
```
\elandscape

\newpage 
\blandscape 
```{r results-education, out.width = "95%", fig.align = 'center', fig.cap = "\\label{fig:results-education}Results: Interaction with Position on Education"}
include_graphics(here("report/figures", "explore-education-1.png"))
```
\elandscape

\newpage 
\blandscape 
```{r results-immigration, out.width = "95%", fig.align = 'center', fig.cap = "\\label{fig:results-immigration}Results: Interaction with Position on Immigration"}
include_graphics(here("report/figures", "explore-immigration-1.png"))
```
\elandscape

### 2021-05-07 src/analysis/Analysis.Rmd
add exploratory results

>>>>

### Ideology
```{r "explore-ideology", echo = F, fig.height= 10, fig.width=20}
source(here("src/analysis/explore_ideology.R"))
p1e + p2e + p3e + plot_layout(ncol=3)
```

### Willingness to Accept Compromise
```{r "explore-wtac", echo = F, fig.height= 10, fig.width=20}
source(here("src/analysis/explore_wtac.R"))
p1e + p2e + p3e + plot_layout(ncol=3)
```

### Attitude towards Women in Politics
```{r "explore-women-politics", echo = F, fig.height= 10, fig.width=20}
source(here("src/analysis/explore_women_politics.R"))
p1e + p2e + p3e + plot_layout(ncol=3)
```

### Position on COVID-19
```{r "explore-covid", echo = F, fig.height= 10, fig.width=20}
source(here("src/analysis/explore_position_covid.R"))
p1e + p2e + p3e + plot_layout(ncol=3)
```

### Position on Defense
```{r "explore-defense", echo = F, fig.height= 10, fig.width=20}
source(here("src/analysis/explore_position_defense.R"))
p1e + p2e + p3e + plot_layout(ncol=3)
```

### Position on Education
```{r "explore-education", echo = F, fig.height= 10, fig.width=20}
source(here("src/analysis/explore_position_education.R"))
p1e + p2e + p3e + plot_layout(ncol=3)
```

### Position on Immigration
```{r "explore-immigration", echo = F, fig.height= 20, fig.width=20}
source(here("src/analysis/explore_position_immigration.R"))
p1e + p2e + p3e + p4e + p5e + p6e + plot_layout(ncol=3)
```
